Scaling rates of true polar wander in convecting planets and moons

### 2016-03-15 response_to_referee.tex

%opening
\title{Response to referee}
\author{Ian Rose and Bruce Buffett}
\date{}

\begin{document}

\maketitle

We thank Yanick Ricard for his thoughtful review.
In addition to several smaller suggestions and corrections,
his review centers on our treatment of the reference frames relevant to the scaling of true polar wander (TPW).
We broadly agree with his criticism, and have substantially reworked our discussion of reference frames to address it.
Several of the key equations have been corrected, and we have changed some of the notation for clarity,
but the overall conclusions of the manuscript are unchanged.

In particular, we have done the following to clarify and correct the treatment of reference frames:
\\
\\
1. We have added a section (Section 2.2) which makes the differences between reference frames explict.
We identify three frames which are important to the problem: 
(1) the inertial, nonrotating frame, 
(2) A body-fixed geographic frame, rotating with respect to the inertial frame with relative rotation vector $\mathbf{\Omega}$, and
(3) The frame described by the principal axes of the convective moment of inertia $\mathbf{E}$, which we call the $\mathbf{E}$-frame.
This frame rotates slowly with respect to the body-fixed frame with rotation vector $\mathbf{\Psi}$.
\\
\\
2. We have added a new figure (Figure 1) which illustrates the different reference frames.
\\
\\
3. We have changed the discussion in Section 2.5 to clarify that the rate of TPW is measured in the body-fixed frame.
The rate of TPW we denote by $\dot{\Theta}$. The physics describing the magnitude of $\dot{\Theta}$ are 
more naturally expressed in the $\mathbf{E}$-frame, with colatitude $\theta$ and longitude $\phi$. 
For much of the discussion we make the simplifying assumption that $\phi=0$.
If the $\mathbf{E}$-frame is not rotating with respect to the body fixed frame ($\mathbf{\Psi}=0$) then $\dot{\Theta} = \dot{\theta}$.
\\
\\
4. We have updated the discussion of the time evolution of the mismatch angle $\theta$ (Section 4.2)
in light of the changes to the reference frames. The characteristic size of $\theta$ is set by 
the competition of its decay via TPW and its growth via $\mathbf{\Psi}$.
This is reflected in Equations (43) and (44).
Our scaling furnishes estimates of the sizes of these two processes.
\\
\\
Besides the discussion of reference frames, we have addressed the following other issues raised in the review:
